---
title: "Homework 3"
author: "PSTAT 131/231"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE)
```

```{r}
library(tidymodels)
library(tidyverse)
library(corrplot)
library(discrim)
library(poissonreg)
library(corrr)
library(klaR)
titanic <- read.csv("titanic.csv")
titanic$survived <- factor(titanic$survived, levels = c("Yes", "No"))
titanic$pclass <- factor(titanic$pclass)
head(titanic)
```
#### Question1 

Split the data, stratifying on the outcome variable, `survived.`  You should choose the proportions to split the data into. Verify that the training and testing data sets have the appropriate number of observations. Take a look at the training data and note any potential issues, such as missing data.

Why is it a good idea to use stratified sampling for this data?

```{r}
set.seed(1979)
titanic_split <- initial_split(titanic, prop = 0.8,
                                strata = survived)
titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)
c(nrow(titanic_train),nrow(titanic_test))
```
The training data sets have 712 observation and testing data sets have 179 observation. They both have the appropriate number of observation

```{r}
library(naniar)
vis_miss(titanic_train)
```
We have 77.81% missing value in cabin and 19.24% in age.

Why is it a good idea to use stratified sampling for this data?
+ Stratified sampling can make a representative amount of each level (No/Yes) of variable (survived) is included in the training and testing data set.


#### Question2

Using the **training** data set, explore/describe the distribution of the outcome variable `survived`.

```{r}
titanic_train %>% 
  ggplot(aes(x = survived)) + 
  geom_bar()
```
There are more died passenger than survived, with 40% dead and 60% survived.

#### Question3 

Using the **training** data set, create a correlation matrix of all continuous variables. Create a visualization of the matrix, and describe any patterns you see. Are any predictors correlated with each other? Which ones, and in which direction?

```{r}
library(corrr)
cor_titanic <- titanic_train %>% 
  select_if(is.numeric) %>% 
  correlate()

cor_titanic %>%
  stretch() %>%
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))))
```
We can also use ggplot and the geom_tile() function to create a heatmap-style correlation plot
Parch is positive correlated with sib_sp with correlation 0.44 
Parch is positive correlated with fare with correlation 0.22
Sib_sp is negative correlated with age with correlation -0.33
Sib_sp is positive correlated with fare with correlation 0.17
Most of variables are not correlated with each other with correlation close to 0


#### Question4

Using the **training** data, create a recipe predicting the outcome variable `survived`. Include the following predictors: ticket class, sex, age, number of siblings or spouses aboard, number of parents or children aboard, and passenger fare.

```{r}
simple_titanic_recipe <-
  recipe(survived ~ pclass+sex+age+sib_sp+parch+fare,data = titanic_train)%>%
  step_impute_linear(age) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_interact(~ fare:starts_with("sex") + age:fare)
```


#### Question5

Specify a **logistic regression** model for classification using the `"glm"` engine. Then create a workflow. Add your model and the appropriate recipe. Finally, use `fit()` to apply your workflow to the **training** data.

```{r}
log_model <- logistic_reg() %>% 
  set_engine("glm")

log_wflow <- workflow() %>% 
  add_model(log_model) %>% 
  add_recipe(simple_titanic_recipe)

log_fit <- fit(log_wflow, titanic_train)
```

#### Question6

**Repeat Question 5**, but this time specify a linear discriminant analysis model for classification using the `"MASS"` engine.

```{r}
lda_mod <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

lda_wkflow <- workflow() %>% 
  add_model(lda_mod) %>% 
  add_recipe(simple_titanic_recipe)

lda_fit <- fit(lda_wkflow, titanic_train)
```

#### Question7 

**Repeat Question 5**, but this time specify a quadratic discriminant analysis model for classification using the `"MASS"` engine.


```{r}
qda_mod <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

qda_wkflow <- workflow() %>% 
  add_model(qda_mod) %>% 
  add_recipe(simple_titanic_recipe)

qda_fit <- fit(qda_wkflow, titanic_train)
```

#### Question8 

**Repeat Question 5**, but this time specify a naive Bayes model for classification using the `"klaR"` engine. Set the `usekernel` argument to `FALSE`.


```{r}
nb_mod <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 

nb_wkflow <- workflow() %>% 
  add_model(nb_mod) %>% 
  add_recipe(simple_titanic_recipe)

nb_fit <- fit(nb_wkflow, titanic_train)
```

#### Question9

Now you've fit four different models to your training data.

Use `predict()` and `bind_cols()` to generate predictions using each of these 4 models and your **training** data. Then use the *accuracy* metric to assess the performance of each of the four models.

Which model achieved the highest accuracy on the training data?

```{r}
predict(log_fit, new_data = titanic_train, type = "prob") %>% 
  bind_cols(titanic_train)
```
```{r}
predict(qda_fit, new_data = titanic_train, type = "prob") %>%
  bind_cols(titanic_train)
```

```{r}
predict(lda_fit, new_data = titanic_train, type = "prob") %>%
  bind_cols(titanic_train)
```
```{r}
# naive Bayes model
predict(nb_fit, new_data = titanic_train, type = "prob") %>%
  bind_cols(titanic_train)
```


```{r}
log_reg_acc <- augment(log_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
```
```{r}
lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
```
```{r}
qda_acc <- augment(qda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
qda_acc
```
```{r}
nb_acc <- augment(nb_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)
nb_acc
```
```{r}
accuracies <- c(log_reg_acc$.estimate, lda_acc$.estimate, 
                nb_acc$.estimate, qda_acc$.estimate)
models <- c("Logistic Regression", "LDA", "Naive Bayes", "QDA")
results <- tibble(accuracies = accuracies, models = models)
results %>% 
  arrange(-accuracies)
```
Logistic Regression achieved highest accuracy on the training data


#### Question 10

Fit the model with the highest training accuracy to the **testing** data. Report the accuracy of the model on the **testing** data.

Again using the **testing** data, create a confusion matrix and visualize it. Plot an ROC curve and calculate the area under it (AUC).

How did the model perform? Compare its training and testing accuracies. If the values differ, why do you think this is so?


```{r}
predict(log_fit, new_data = titanic_test, type = "prob")
```

```{r}
multi_metric <- metric_set(accuracy, sensitivity, specificity)

augment(log_fit, new_data = titanic_test) %>%
  multi_metric(truth = survived, estimate = .pred_class) 

```
The accuracy of the model on the testing data is 0.7988827

```{r}
augment(log_fit, new_data = titanic_test) %>%
  conf_mat(truth = survived, estimate = .pred_class) %>%
  autoplot(type = "heatmap")
```

```{r}
augment(log_fit, new_data = titanic_test) %>%
  roc_curve(survived, .pred_Yes) %>%
  autoplot()
```
```{r}
augment(log_fit, new_data = titanic_test) %>%
  roc_auc(survived, .pred_Yes)
```
The model preforms well, and the area under ROC-curve is 0.86. The accuracy between training and testing is similar and both close to 80.




